On the power of oritatami cotranscriptional folding with unary bead sequence\thanks{This work is supported in part by KAKENHI Grant-in-Aid for Challenging Research (Exploratory) No.~18K19779 and JST Program to Disseminate Tenure Tracking System No.~6F36 granted to S.~Z.~F. and S.~S.}

### 2018-12-03 arity1.tex
Changes to pyramid
I am working on the drawing now to change the colors to numbers.

\subsection{$\alpha = 1$, arbitrary alphabets}
First we present a lower bound construction for arity $\alpha=1$ systems. At $\alpha=1$, allowing delay $\delta=2$ increases the power of OS compared with $\delta=1$, if at least four bead types are allowed. We demonstrate this with an infinite family of OS, which fold deterministically a transcript of length $\frac{(n-1)^2}{4}$ starting from a given seed of length $n$.

@@

\noindent The transcript is
\begin{center}

	%\scriptsize
	\begin{tabular}{llll}
		& $k$ odd &  & $k$ even\\
		$w=$\hspace{1cm} & $(2413)^{k-1}241$ & \hspace{1cm} &  $(2413)^{k-1}241$\\
		     & $(4231)^{k-1}4$   & &  $(4231)^{k-1}4$  \\
		     & $(1324)^{k-2}132$ & &  $(1324)^{k-2}132$\\
		     & $(3142)^{k-2}3$   & &  $(3142)^{k-2}3$ \vspace{5pt}\\

		     & $(2413)^{k-3}241$ & &  $(2413)^{k-3}241$\\
		     & $(4231)^{k-3}4$   & &  $(4231)^{k-3}4$  \\
		     & $(1324)^{k-4}132$ & &  $(1324)^{k-4}132$\\
		     & $(3142)^{k-4}3$   & &  $(3142)^{k-4}3$\\
			 & \vdots			 & &  \vdots\\
			 & $(2413)^{2} 241$	 & &  $(2413)^{1} 241$\\
			 & $(4231)^2 4$		 & &  $(4231)^1 4$\\
			 & $(1324)^1 132$	 & &  $(1324)^0 132$\\
			 & $(3142)^1 3$		 & &  $(3142)^0 3$\\
			 & $(2413)^0 241$	 & & \\
			 & $(4231)^0 4$  	 & 
	\end{tabular}

\end{center}
The transcript above is written in rows which correspond to beads in the conformation stabilized along the same row on the grid. To simplify the argument we will use \textit{row} both for the transcript above and for the conformation it stabilizes in. In line with this, row $\ell\in \{1,\dots, 2k\}$ is as follows:  
\begin{center}
	\begin{tabular}{llll}
							& row $\ell$ & 			& $\ell\mod 4$ \\
			& $(2413)^{k-\lfloor (\ell+1)/2\rfloor}241$ & \hspace{1cm} &  $\ell\equiv 1\mod 4$\\
							& $(4231)^{k-\lfloor (\ell+1)/2\rfloor}4$   & &  $\ell\equiv 2 \mod 4$ \\
							& $(1324)^{k-\lfloor (\ell+1)/2\rfloor}132$ & &  $\ell\equiv 3 \mod 4$\\
							& $(3142)^{k-\lfloor (\ell+1)/2\rfloor}3$   & &  $\ell\equiv 4 \mod 4$ 
	\end{tabular}
\end{center}
so $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$. Row $1$ is of length $4k-1$ and row $\ell+1$ is two beads shorter than row $\ell$, so the length of the whole transcript is $|w|=4k^2=\frac{(4k+1-1)^2}{4}=\frac{(|\sigma|-1)^2}{4}$. As an example, see Fig.~\ref{CI:big}, where $k=5$, so the length of the seed is $4k+1=21$ and the transcript is $4k^2 = 100$ beads long.

>>>>

\subsection{$\alpha = 1$, arbitrary alphabets}
First we present a lower bound construction for arity $1$ systems. At $\alpha=1$, having delay $\delta=2$ allows the deterministic folding of quadratic length transcripts compared with $\delta=1$, where, as stated before, the maximum length is linear in the length of the seed. We demonstrate this with an infinite family of OS, which fold deterministically a transcript of length $\frac{(n-1)^2}{4}$ starting from a given seed of length $n$.

@@

The transcript is $w=\mathrm{row}_1\cdots \mathrm{row}_{2k}$, where $\mathrm{row}_\ell$, for $\ell\in \{1,\dots, 2k\}$ is given in the table below.

\begin{figure}
	\begin{minipage}{.49\textwidth}
		%\centering
		\begin{tabular}{l|l}
			\multicolumn{2}{c}{Transcript $w$}\\
			\multicolumn{2}{c}{}  \\
			$k$ odd & \hspace{0.3cm} $k$ even\\\hline
			& \\
			$(2413)^{k-1}241$\hspace{0.3cm} & \hspace{0.3cm} $(2413)^{k-1}241$\\
			$(4231)^{k-1}4$   &  \hspace{0.3cm} $(4231)^{k-1}4$  \\
			$(1324)^{k-2}132$ &  \hspace{0.3cm} $(1324)^{k-2}132$\\
			$(3142)^{k-2}3$   &  \hspace{0.3cm} $(3142)^{k-2}3$ \\
			\vdots			 &  \hspace{0.3cm} \vdots\\
			$(1324)^1 132$	 &  \hspace{0.3cm} $(2413)^{1} 241$\\
			$(3142)^1 3$		 & \hspace{0.3cm} $(4231)^1 4$\\
			$(2413)^0 241$	 &  \hspace{0.3cm} $(1324)^0 132$\\
			$(4231)^0 4$		 & \hspace{0.3cm} $(3142)^0 3$\\
		\end{tabular}
	\end{minipage}
	%\scriptsize
	\begin{minipage}{.49\textwidth}
		%\centering
		\begin{tabular}{|l|c|}
			\hline
			\hspace{1.2cm}row $\ell$ & $\ell\mod 4$ \\\hline
			 & \\
			\hspace{0.1cm}$(2413)^{k-\lfloor (\ell+1)/2\rfloor}241$ \hspace{0.1cm} &  $\textrm{ }\ell\equiv 1\mod 4\textrm{ }$\\
			\hspace{0.1cm}$(4231)^{k-\lfloor (\ell+1)/2\rfloor}4$   &  $\textrm{ }\ell\equiv 2 \mod 4\textrm{ }$ \\
			\hspace{0.1cm}$(1324)^{k-\lfloor (\ell+1)/2\rfloor}132$ &  $\textrm{ }\ell\equiv 3 \mod 4\textrm{ }$ \\
			\hspace{0.1cm}$(3142)^{k-\lfloor (\ell+1)/2\rfloor}3$   &  $\textrm{ }\ell\equiv 4 \mod 4\textrm{ }$ \\\hline
		\end{tabular}

	\end{minipage}

%\begin{center}
%	
%	%\scriptsize
%	\begin{tabular}{llll}
%		& $k$ odd &  & $k$ even\\
%		$w=$\hspace{1cm} & $(2413)^{k-1}241$ & \hspace{1cm} &  $(2413)^{k-1}241$\\
%		     & $(4231)^{k-1}4$   & &  $(4231)^{k-1}4$  \\
%		     & $(1324)^{k-2}132$ & &  $(1324)^{k-2}132$\\
%		     & $(3142)^{k-2}3$   & &  $(3142)^{k-2}3$ \vspace{5pt}\\
%		     
%		     & $(2413)^{k-3}241$ & &  $(2413)^{k-3}241$\\
%		     & $(4231)^{k-3}4$   & &  $(4231)^{k-3}4$  \\
%		     & $(1324)^{k-4}132$ & &  $(1324)^{k-4}132$\\
%		     & $(3142)^{k-4}3$   & &  $(3142)^{k-4}3$\\
%			 & \vdots			 & &  \vdots\\
%			 & $(2413)^{2} 241$	 & &  $(2413)^{1} 241$\\
%			 & $(4231)^2 4$		 & &  $(4231)^1 4$\\
%			 & $(1324)^1 132$	 & &  $(1324)^0 132$\\
%			 & $(3142)^1 3$		 & &  $(3142)^0 3$\\
%			 & $(2413)^0 241$	 & & \\
%			 & $(4231)^0 4$  	 & 
%	\end{tabular}
%	
%\end{center}

The transcript above is written in rows which correspond to beads in the conformation stabilized along the same row on the grid. To simplify the argument we will use \textit{row} both for the transcript above and for the conformation it stabilizes in (note that in the figure the row index grows from bottom to top).

Row $1$ is of length $4k-1$ and row $\ell+1$ is two beads shorter than row $\ell$, so the length of the whole transcript is $|w|=4k^2=\frac{(4k+1-1)^2}{4}=\frac{(|\sigma|-1)^2}{4}$. As an example, see Fig.~\ref{CI:big}, where $k=5$, so the length of the seed is $4k+1=21$ and the transcript is $4k^2 = 100$ beads long.
